{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-02-10 documents/background.tex
Oh hey the brilluoin just had a bug

See the section on pulse artifacts. Electrode insulation is not mentioned, so electrochemical effects are possible but unlikely given the short duration of the pulses. The observed RNA damage is unexpected from a mechanical standpoint but is somewhat like the damage due to copper ions found by \cite{Microwave1987}; therefore electrochemical interaction may have been a confounding factor.

@@

\subsection{Electrorotation}

@@

Rotation is sub-synchronous at a few Hz, whereas the field rotates at between 0.1 MHz to over 50 MHz; in all cases the frequency is made high enough that

>>>>

See the section on pulse artifacts. Electrode insulation is not mentioned, so electrochemical effects are possible. The observed RNA damage is unexpected from a mechanical standpoint but is somewhat like the damage due to copper ions found by \cite{Microwave1987}; therefore electrochemical interaction may have been a confounding factor.

@@

\subsection{Dielectrophoresis and electrorotation}

@@

Rotation is sub-synchronous at a few dozen Hz, whereas the field rotates at between 0.1 MHz to over 50 MHz; in most cases the frequency is made high enough that ion does not occur.

### 2021-02-10 documents/brillouin_pulse_math.tex
words
Oh hey the brilluoin just had a bug

While it is clearly possible to produce this abnormal penetration (any sharp edge sufficiently distant from  suffices to produce a dispersive pulse), it was not obvious to us that a waveform 
could be constructed that would be an effective driver for the normal modes in question. 
Oughston ; if the pulses are too close together, they interfere as they propagate and distort the precursor thus formed.

For instance, despite the waveform from nonlinear transmission lines producing strong wideband components, in cursory simulations they did not appear to satisfy the requirements for Brillouin pulses\wikinote{dubious-discuss}\wikinote{citation-needed}. Our working hypothesis is that this is because of destructive interference from the falling edge that immediately follows; but this is mere speculation.\wikinote{dubious-discuss}

@@

However, the energy contained in such a standard pulsed-sine or gaussian train decays very quickly,

@@

\pagebreak
A qualitative statement of the problem we were trying to solve (which may not be correct, especially if Q turns out to be < 1):

@@

Of course, 10x attenuation at 1 MV/m still takes us outside. However, the loss that makes phased-array near-field focusing systems impractical at baseband is no longer a concern. A dispersive phased array with more than 10 elements may allow the complete elimination of attenuation without exceeding the limit field at any point in the body.

>>>>

While it is clearly possible to produce this abnormal penetration (any sharp edge sufficiently distant from  suffices to produce a dispersive pulse), it was not obvious to us that a waveform 
could be constructed that would be an effective driver for the normal modes in question.

First, Oughston ; if the pulses are too close together, they interfere as they propagate and distort the precursor thus formed.

As an example, despite the waveform from nonlinear transmission lines producing strong wideband components, in cursory simulations they did not appear to satisfy the requirements for Brillouin pulses\wikinote{dubious-discuss}\wikinote{citation-needed}. Our working hypothesis is that this is because of destructive interference from the falling edge that immediately follows; but this is mere speculation.\wikinote{dubious-discuss}

Second, while the pulse amplitude decays slowly, the total energy contained in such a precursor decays very quickly. The biological ramfications of discussed in detail by Adair in \cite{Biophysics2000}.

@@

@@

\pagebreak
A qualitative statement of the problem we were trying to solve (which may not a useful formulation, especially if Q turns out to be < 1 and the virus exhibits only relaxational and non-resonant behavior):

@@

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\includesvg[width=\textwidth]{propagated_waveforms}
	\caption{}
\end{figure}

Of course, 10x attenuation at 1 MV/m still takes us beyond safe levels at the skin. However, the loss that makes phased-array near-field focusing systems impractical at baseband is no longer a concern. A dispersive phased array with more than 10 elements may allow the complete elimination of attenuation without exceeding the limit field at any point in the body.

### 2021-02-10 documents/detection.tex
Oh hey the brilluoin just had a bug

\begin{autem}
	I hasten to note that quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs. The amount of time and effort we spent on this problem was completely unjustifiable. It was driven by an acute lack of competence, equipment, and the 0.8 uL volume constraints of our original poorly designed microwave setup.\\

@@

@@

A lot of the basic facts of phage were determined in the 1930s;

@@

@@

@@

Otherwise, GFP-flouresecent strains of E. coli, or phage which has been labelled with a

@@

Concentrated can be put into the microgram range of many standard protein assays like BCA, but that requires propagation and PEG precipitation, plus many such assays pose disposal hazards and stain labware.

>>>>

\begin{autem}
	I hasten to note that culturing and quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs. The amount of time and effort we spent on this problem was completely unjustifiable. It was driven by an acute lack of competence, equipment, and the 0.8 uL volume constraints of our original poorly designed microwave setup.\\

@@

Most of our results are tainted by two factors:

First, the fridge froze. A small "three-way"

@@

A lot of the basic facts of phage, and most of the useful techniques were determined in the 1930s.

@@

Otherwise, GFP-flouresecent strains of E. coli, or phage which has been labeled with a

@@

X-gal is only soluble in DMF and DMSO. We choose DMSO due to DMF's toxicity. DMSO is miscible with water, so that works out nicely. Solutions of < 0.75\% DMSO seem to not be cytotoxic.

@@

@@

Early workers on phage mention\cite{ADSORPTION1940}  that cultures with a titer above about $10^10$ have an opalescent blue tint due to Tyndall scattering. Schlesinger in 1933 \cite{Beobachtung1933} (paper is in German). This technique appears to have been forgotten?

Concentrated can be put into the microgram range of high-sensitivity protein assays like BCA or Bradford, but that requires propagation and PEG precipitation, plus many such assays pose disposal hazards and stain labware.
